### 2023-03-09 manuscript.tex
Fixing table [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b85d18073a2e39374aa8bd2e77e5046947734a25.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b85d18073a2e39374aa8bd2e77e5046947734a25/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4378805497

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d}{SORTEE-Github-Hackathon/manuscript@b7b98e0}
on March 9, 2023.

@@

@@

A comparison of technologies commonly used for collaborating on research
in Ecology and Evolutionary Biology. In the first column, we group
platforms for collaboration into broad guilds. The second column lists
the platform for collaboration. The remaining columns indicate whether
the platform for collaboration includes certain features \{\#tbl:compare\}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b85d18073a2e39374aa8bd2e77e5046947734a25/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b85d18073a2e39374aa8bd2e77e5046947734a25}{SORTEE-Github-Hackathon/manuscript@b85d180}
on March 9, 2023.

@@

\caption{A comparison of technologies commonly used for collaborating on research
in Ecology and Evolutionary Biology. In the first column, we group
platforms for collaboration into broad guilds. The second column lists
the platform for collaboration. The remaining columns indicate whether
the platform for collaboration includes certain features \label{tbl:compare}}\label{tbl:compare}\tabularnewline
\endfirsthead

@@
